Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-07 supp/02-2dgm-rawmat.Rmd
<edit index>

Elliptical bifaces from the Millsap Cache and Jowell Farm were used to examine whether their morphology remains stable, or expresses morphological variability by site/raw meterial. Variability in elliptical biface morphology provides evidence associated with differences in morphology as a function of geography/raw material.

@@

# allometry
anova(fit.size)
```

>>>>

Elliptical bifaces from the Millsap Cache and Jowell Farm were used to examine whether their morphology remains stable, or expresses morphological variability by site/raw material. Variability in elliptical biface morphology provides evidence associated with differences in morphology as a function of geography/raw material.

@@

# shape change with size?
anova(fit.size)
```

### 2022-11-07 supp/03-2dgm-sizeclass.Rmd
<edit index>

Two `size classes` (large/small) were used to assess whether the morphology of elliptical bifaces from Millsap Cache and Jowell Farm remains morphologically stable through reduction

>>>>

Two `size classes` (large/small) were used to assess whether the morphology of elliptical bifaces from Millsap Cache and Jowell Farm remains morphologically stable/consistent through reduction.
